MLB Team Statistics between 2000 - 2023 on Predicting Games Won per Season ^[Code and data are available at: https://github.com/YcartXin/MLB_Team_Stats]

### 2024-04-03 paper/paper.qmd
Progressing on introduction

---
title: "MLB Team Statistics between 2012 - 2018 on Predicting Games Won per Season ^[Code and data are available at: https://github.com/YcartXin/MLB_Team_Stats"
author: 
  - Tracy Yang
date: today
date-format: long
abstract: "hehe."
format: 
  typst:
    toc: true
number-sections: true
bibliography: references.bib
---
```{r}
#| include: false
#| warning: false
#| message: false

@@

Behind the entertaining personalities and eye-catching traditions of baseball is a game where teams and are meticulously crafted with calculation. Baseball's fascination with numbers persisted since its creation (Swhwarz, 2004). Runs scored have always been recorded to evaluate performance, while other statistics developed overtime into the complicated net of data that now reside upon the MLB official site (). However, a team's performance can differ greatly year to year. A team's last year wins are not often indicative of the coming season. Many factors play into the seasonal performance of a team including more unpredictable variables such as injuries, and luck. However, with the common narrative of baseball being a numbers game, we aim to estimate the impact of important statistics of a team on its games won per season, more specifically, the progressing 2024 season.

@@

The remainder of this paper is structured as follows. @sec-data....
We examine the Major League Baseball team data from 2012 to 2018 focusing on a team's batting average (AVG), defensive efficiency ratio (DER), and earned run average (ERA) to predict the number of games a team would win out of 162 in a season. We estimate an Bayesian hierarchical model which explains their attributes based on their functionality.

@@

\appendix

# Appendix {-}

>>>>

---
title: "MLB Team Statistics between 2000 - 2023 on Predicting Games Won per Season ^[Code and data are available at: https://github.com/YcartXin/MLB_Team_Stats]"
author: 
  - Tracy Yang
date: today
date-format: long
abstract: "Using MLB key team statistics between 2000 and 2023, this paper investigates the outcome of the 2024 season using each team's current statistics on predicting their total wins out of 162 games. We also investigate the common conception that baseball is a numbers game by evaluating the predictability of wins that a team would obtain during a seasion from looking at their batting average (AVG), defensive efficiency ratio (DER), and earned run average (ERA)."
format: 
  typst:
    toc: true
number-sections: true
bibliography: references.bib
---
```{r}
#| include: false
#| warning: false
#| message: false

@@

Behind the entertaining personalities and eye-catching traditions of baseball is a game where teams and are meticulously crafted with calculation. Baseball's fascination with numbers persisted since its creation (Swhwarz, 2004). Runs scored have always been recorded to evaluate performance, while other statistics developed overtime into the complicated net of data that now reside upon the MLB official site (XX). The term "sabermetrics" even developed to describe in specific baseball statistics (XX) However, a team's performance can differ greatly year to year. A team's last year wins are not often indicative of the coming season. Many factors play into the seasonal performance of a team including more unpredictable variables such as injuries, and luck. However, with the common narrative of baseball being a numbers game, we aim to estimate the impact of important statistics of a team on its games won per season, more specifically, the progressing 2024 season.

Important statistics for a team in this paper is defined as the team's batting average (AVG), defensive efficiency ratio (DER), and earned run average (ERA). These three statistics each refer to an important aspect of a strong team: hitting, pitching, and fielding prospectively. The specifics of these indicators will be elaborated on in @sec-data. Many 2024 season predictions exist...

@@

@@
